---
title: "Developing Data Product Course Project"
author: "Dahj Muwawa JN"
date: "September 17, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r loadinglib, include=FALSE}
  library(shiny)
  library(caret)
  library(rattle)
  library(rpart.plot)
  library(ggplot2)
  library(dplyr)
  library(C50)
```
## Telecoms Churn Prediction using Logical Regression Model
Part of the final project for building Data Product. We classify customers to churn. 
The basic steps are as follow:

1. Loading the Churn dataset from the C50 package
```{r loadind data, comment="", echo=TRUE}
data(churn)
```
2. Do an EDA to evaluate relationships between variables.
3. Train the datasets without & with cross validation
4. Check the accuracy of the above, build the prediction trees and Predict the new value based on the two model. 
Note that due to the limited number of slides, not all output will be shown. 

## Building the Models
Building a Regression Model with no Cross Validation

```{r regression, comment="", echo=TRUE}
   modFit=train(churn~., method="rpart", data=churnTrain)
   lpartpred=predict(modFit, newdata = churnTest)
   confusionMatrix(lpartpred, churnTest$churn)
```
## Applying Cross Validation
With K=10 as the default. On the shiny app, the user can slide the slider 
to choose the K value

```{r cross-validation, comment="", echo=TRUE}
folds=createFolds(y=churnTrain$churn, k=10, list = TRUE, returnTrain = FALSE)
trainfolds=churnTrain[folds$Fold01,]
modFit_rpart_c=train(churn~., method="rpart", data=trainfolds)
lpart_cross_pred=predict(modFit_rpart_c, newdata = churnTest)
confusionMatrix(lpart_cross_pred, churnTest$churn)
```
## Decision Tree of the Model
```{r decision, comment="", echo=TRUE}
  fancyRpartPlot(modFit$finalModel)
```